\poemtitle{A Song}

\begin{poem}

\begin{stanza}
Sweet dreams, form a shade\verseline
O'er my lovely infant's head!\verseline
Sweet dreams of pleasant streams\verseline
By happy, silent, moony beams!
\end{stanza}
\begin{stanza}
Sweet Sleep, with soft down\verseline
Weave thy brows an infant crown\verseline
Sweet Sleep, angel mild,\verseline
Hover o'er my happy child!
\end{stanza}
\begin{stanza}
Sweet smiles, in the night\verseline
Hover over my delight!\verseline
Sweet smiles, mother's smile,\verseline
All the livelong night beguile.
\end{stanza}
\begin{stanza}
Sweet moans, dovelike sighs,\verseline
Chase not slumber from thine eyes!\verseline
Sweet moan, sweeter smile,\verseline
All the dovelike moans beguile.
\end{stanza}
\begin{stanza}
Sleep, sleep, happy child!\verseline
All creation slept and smiled.\verseline
Sleep, sleep, happy sleep,\verseline
While o'er thee doth mother weep.
\end{stanza}
\begin{stanza}
Sweet babe, in thy face\verseline
Holy image I can trace;\verseline
Sweet babe, once like thee\verseline
Thy Maker lay, and wept for me:
\end{stanza}
\begin{stanza}
Wept for me, for thee, for all,\verseline
When He was an infant small.\verseline
Thou His image ever see,\verseline
Heavenly face that smiles on thee!
\end{stanza}
\begin{stanza}
Smiles on thee, on me, on all,\verseline
Who became an infant small;\verseline
Infant smiles are his own smiles;\verseline
Heaven and earth to peace beguiles.
\end{stanza}

\end{poem}\poemtitle{The Little Girl Lost}

\begin{poem}

\begin{stanza}
In futurity\verseline
I prophetic see\verseline
That the earth from sleep\verseline
(Grave the sentence deep)
\end{stanza}
\begin{stanza}
\verseindent Shall arise, and seek\verseline
for her Maker meek;\verseline
And the desert wild\verseline
Become a garden mild.
\end{stanza}
\begin{stanza}
\verseindent In the southern clime,\verseline
Where the summer's prime\verseline
Never fades away,\verseline
Lovely Lyca lay.
\end{stanza}
\begin{stanza}
\verseindent Seven summers old\verseline
Lovely Lyca told.\verseline
She had wandered long,\verseline
Hearing wild birds' song.
\end{stanza}
\begin{stanza}
\verseindent "Sweet sleep, come to me\verseline
Underneath this tree;\verseline
Do father, mother, weep?\verseline
Where can Lyca sleep?
\end{stanza}
\begin{stanza}
\verseindent "Lost in desert wild\verseline
Is your little child.\verseline
How can Lyca sleep\verseline
If her mother weep?
\end{stanza}
\begin{stanza}
\verseindent "If her heart does ache,\verseline
Then let Lyca wake;\verseline
If my mother sleep,\verseline
Lyca shall not weep.
\end{stanza}
\begin{stanza}
\verseindent "Frowning, frowning night,\verseline
O'er this desert bright\verseline
Let thy moon arise,\verseline
While I close my eyes."
\end{stanza}
\begin{stanza}
\verseindent Sleeping Lyca lay\verseline
While the beasts of prey,\verseline
Come from caverns deep,\verseline
Viewed the maid asleep.
\end{stanza}
\begin{stanza}
\verseindent The kingly lion stood,\verseline
And the virgin viewed:\verseline
Then he gambolled round\verseline
O'er the hallowed ground.
\end{stanza}
\begin{stanza}
\verseindent Leopards, tigers, play\verseline
Round her as she lay;\verseline
While the lion old\verseline
Bowed his mane of gold,
\end{stanza}
\begin{stanza}
\verseindent And her breast did lick\verseline
And upon her neck,\verseline
From his eyes of flame,\verseline
Ruby tears there came;
\end{stanza}
\begin{stanza}
\verseindent While the lioness\verseline
Loosed her slender dress,\verseline
And naked they conveyed\verseline
To caves the sleeping maid.
\end{stanza}

\end{poem}\poemtitle{Earth's Answer}

\begin{poem}

\begin{stanza}
Earth raised up her head
From the darkness dread and drear,
Her light fled,
Stony, dread,
And her locks covered with grey despair.
\end{stanza}
\begin{stanza}
"Prisoned on watery shore,
Starry jealousy does keep my den
Cold and hoar;
Weeping o'er,
I hear the father of the ancient men.
\end{stanza}
\begin{stanza}
"Selfish father of men!
Cruel, jealous, selfish fear!
Can delight,
Chained in night,
The virgins of youth and morning bear?
\end{stanza}
\begin{stanza}
"Does spring hide its joy,
When buds and blossoms grow?
Does the sower
Sow by night,
Or the plowman in darkness plough?
\end{stanza}
\begin{stanza}
"Break this heavy chain,
That does freeze my bones around!
Selfish, vain,
Eternal bane,
That free love with bondage bound."
\end{stanza}

\end{poem}\poemtitle{The Tyger}

\begin{poem}

\begin{stanza}
Tyger, tyger, burning bright\verseline
In the forests of the night,\verseline
What immortal hand or eye\verseline
Could frame thy fearful symmetry?
\end{stanza}
\begin{stanza}
\verseindent In what distant deeps or skies\verseline
Burnt the fire of thine eyes?\verseline
On what wings dare he aspire?\verseline
What the hand dare seize the fire?
\end{stanza}
\begin{stanza}
\verseindent And what shoulder and what art\verseline
Could twist the sinews of thy heart?\verseline
And, when thy heart began to beat,\verseline
What dread hand and what dread feet?
\end{stanza}
\begin{stanza}
\verseindent What the hammer? what the chain?\verseline
In what furnace was thy brain?\verseline
What the anvil? what dread grasp\verseline
Dare its deadly terrors clasp?
\end{stanza}
\begin{stanza}
\verseindent When the stars threw down their spears,\verseline
And watered heaven with their tears,\verseline
Did he smile his work to see?\verseline
Did he who made the lamb make thee?
\end{stanza}
\begin{stanza}
\verseindent Tyger, tyger, burning bright\verseline
In the forests of the night,\verseline
What immortal hand or eye\verseline
Dare frame thy fearful symmetry?
\end{stanza}

\end{poem}