\poemtitle{Night}

\begin{poem}

\begin{stanza}
\verseindent The sun descending in the west,\verseline
The evening star does shine;\verseline
The birds are silent in their nest,\verseline
And I must seek for mine.\verseline
\verseindent The moon, like a flower\verseline
\verseindent In heaven's high bower,\verseline
\verseindent With silent delight,\verseline
\verseindent Sits and smiles on the night.
\end{stanza}
\begin{stanza}
\verseindent Farewell, green fields and happy grove,\verseline
Where flocks have ta'en delight.\verseline
Where lambs have nibbled, silent move\verseline
The feet of angels bright;\verseline
\verseindent Unseen they pour blessing,\verseline
\verseindent And joy without ceasing,\verseline
\verseindent On each bud and blossom,\verseline
\verseindent And each sleeping bosom.
\end{stanza}
\begin{stanza}
\verseindent They look in every thoughtless nest\verseline
Where birds are covered warm;\verseline
They visit caves of every beast,\verseline
To keep them all from harm:\verseline
\verseindent If they see any weeping\verseline
\verseindent That should have been sleeping,\verseline
\verseindent They pour sleep on their head,\verseline
\verseindent And sit down by their bed.
\end{stanza}
\begin{stanza}
\verseindent When wolves and tigers howl for prey,\verseline
They pitying stand and weep;\verseline
Seeking to drive their thirst away,\verseline
And keep them from the sheep.\verseline
\verseindent But, if they rush dreadful,\verseline
\verseindent The angels, most heedful,\verseline
\verseindent Receive each mild spirit,\verseline
\verseindent New worlds to inherit.
\end{stanza}
\begin{stanza}
\verseindent And there the lion's ruddy eyes\verseline
Shall flow with tears of gold:\verseline
And pitying the tender cries,\verseline
And walking round the fold:\verseline
\verseindent Saying: "Wrath by His meekness,\verseline
\verseindent And, by His health, sickness,\verseline
\verseindent Are driven away\verseline
\verseindent From our immortal day.
\end{stanza}
\begin{stanza}
\verseindent "And now beside thee, bleating lamb,\verseline
I can lie down and sleep,\verseline
Or think on Him who bore thy name,\verseline
Graze after thee, and weep.\verseline
\verseindent For, washed in life's river,\verseline
\verseindent My bright mane for ever\verseline
\verseindent Shall shine like the gold,\verseline
\verseindent As I guard o'er the fold."
\end{stanza}

\end{poem}