\poemtitle{The Chimney-Sweeper}

\begin{poem}

\begin{stanza}
When my mother died I was very young,\verseline
And my father sold me while yet my tongue\verseline
Could scarcely cry "Weep! weep! weep! weep!"\verseline
So your chimneys I sweep, and in soot I sleep.
\end{stanza}
\begin{stanza}
\verseindent There's little Tom Dacre, who cried when his head,\verseline
That curled like a lamb's back, was shaved; so I said,\verseline
"Hush, Tom! never mind it, for, when your head's bare,\verseline
You know that the soot cannot spoil your white hair."
\end{stanza}
\begin{stanza}
\verseindent And so he was quiet, and that very night,\verseline
As Tom was a-sleeping, he had such a sight!—\verseline
That thousands of sweepers, Dick, Joe, Ned, and Jack,\verseline
Were all of them locked up in coffins of black.
\end{stanza}
\begin{stanza}
\verseindent And by came an angel, who had a bright key,\verseline
And he opened the coffins, and let them all free;\verseline
Then down a green plain, leaping, laughing, they run,\verseline
And wash in a river, and shine in the sun.
\end{stanza}
\begin{stanza}
\verseindent Then naked and white, all their bags left behind,\verseline
They rise upon clouds, and sport in the wind;\verseline
And the Angel told Tom, if he'd be a good boy,\verseline
He'd have God for his father, and never want joy.
\end{stanza}
\begin{stanza}
\verseindent And so Tom awoke, and we rose in the dark,\verseline
And got with our bags and our brushes to work.\verseline
Though the morning was cold, Tom was happy and warm:\verseline
So, if all do their duty, they need not fear harm.
\end{stanza}
\begin{stanza}