\poemtitle{The Little Girl Lost}

\begin{poem}

\begin{stanza}
In futurity\verseline
I prophetic see\verseline
That the earth from sleep\verseline
(Grave the sentence deep)
\end{stanza}
\begin{stanza}
\verseindent Shall arise, and seek\verseline
for her Maker meek;\verseline
And the desert wild\verseline
Become a garden mild.
\end{stanza}
\begin{stanza}
\verseindent In the southern clime,\verseline
Where the summer's prime\verseline
Never fades away,\verseline
Lovely Lyca lay.
\end{stanza}
\begin{stanza}
\verseindent Seven summers old\verseline
Lovely Lyca told.\verseline
She had wandered long,\verseline
Hearing wild birds' song.
\end{stanza}
\begin{stanza}
\verseindent "Sweet sleep, come to me\verseline
Underneath this tree;\verseline
Do father, mother, weep?\verseline
Where can Lyca sleep?
\end{stanza}
\begin{stanza}
\verseindent "Lost in desert wild\verseline
Is your little child.\verseline
How can Lyca sleep\verseline
If her mother weep?
\end{stanza}
\begin{stanza}
\verseindent "If her heart does ache,\verseline
Then let Lyca wake;\verseline
If my mother sleep,\verseline
Lyca shall not weep.
\end{stanza}
\begin{stanza}
\verseindent "Frowning, frowning night,\verseline
O'er this desert bright\verseline
Let thy moon arise,\verseline
While I close my eyes."
\end{stanza}
\begin{stanza}
\verseindent Sleeping Lyca lay\verseline
While the beasts of prey,\verseline
Come from caverns deep,\verseline
Viewed the maid asleep.
\end{stanza}
\begin{stanza}
\verseindent The kingly lion stood,\verseline
And the virgin viewed:\verseline
Then he gambolled round\verseline
O'er the hallowed ground.
\end{stanza}
\begin{stanza}
\verseindent Leopards, tigers, play\verseline
Round her as she lay;\verseline
While the lion old\verseline
Bowed his mane of gold,
\end{stanza}
\begin{stanza}
\verseindent And her breast did lick\verseline
And upon her neck,\verseline
From his eyes of flame,\verseline
Ruby tears there came;
\end{stanza}
\begin{stanza}
\verseindent While the lioness\verseline
Loosed her slender dress,\verseline
And naked they conveyed\verseline
To caves the sleeping maid.
\end{stanza}

\end{poem}