\poemtitle{The Little Girl Found}

\begin{poem}

\begin{stanza}
All the night in woe\verseline
Lyca's parents go\verseline
Over valleys deep,\verseline
While the deserts weep.
\end{stanza}
\begin{stanza}
\verseindent Tired and woe-begone,\verseline
Hoarse with making moan,\verseline
Arm in arm, seven days\verseline
They traced the desert ways.
\end{stanza}
\begin{stanza}
\verseindent Seven nights they sleep\verseline
Among shadows deep,\verseline
And dream they see their child\verseline
Starved in desert wild.
\end{stanza}
\begin{stanza}
\verseindent Pale through pathless ways\verseline
The fancied image strays,\verseline
Famished, weeping, weak,\verseline
With hollow piteous shriek.
\end{stanza}
\begin{stanza}
\verseindent Rising from unrest,\verseline
The trembling woman pressed\verseline
With feet of weary woe;\verseline
She could no further go.
\end{stanza}
\begin{stanza}
\verseindent In his arms he bore\verseline
Her, armed with sorrow sore;\verseline
Till before their way\verseline
A couching lion lay.
\end{stanza}
\begin{stanza}
\verseindent Turning back was vain:\verseline
Soon his heavy mane\verseline
Bore them to the ground,\verseline
Then he stalked around,
\end{stanza}
\begin{stanza}
\verseindent Smelling to his prey;\verseline
But their fears allay\verseline
When he licks their hands,\verseline
And silent by them stands.
\end{stanza}
\begin{stanza}
\verseindent They look upon his eyes,\verseline
Filled with deep surprise;\verseline
And wondering behold\verseline
A spirit armed in gold.
\end{stanza}
\begin{stanza}
\verseindent On his head a crown,\verseline
On his shoulders down\verseline
Flowed his golden hair.\verseline
Gone was all their care.
\end{stanza}
\begin{stanza}
\verseindent "Follow me," he said;\verseline
"Weep not for the maid;\verseline
In my palace deep,\verseline
Lyca lies asleep."
\end{stanza}
\begin{stanza}
\verseindent Then they followed\verseline
Where the vision led,\verseline
And saw their sleeping child\verseline
Among tigers wild.
\end{stanza}
\begin{stanza}
\verseindent To this day they dwell\verseline
In a lonely dell,\verseline
Nor fear the wolvish howl\verseline
Nor the lion's growl.
\end{stanza}

\end{poem}